Computational biology in the 21st century:\\Scaling with compressive algorithms

### 2015-09-20 main.tex
Reworded last paragraph to be a bit more upbeat

\textbf{rewrite paragraph}
While this Review has focused on the importance of algorithms that leverage the
structure of data to cope with the increased throughput in computational 
biology, it is also essential that techniques continue to make better 
predictions and models that demonstrate improved fidelity to wet-lab 
experiments.

\section{Acknowledgements}
This work is supported by the National Institutes of Health, under
grant GM108348.
Y.W.Y. is supported by a Hertz Fellowship.

>>>>

The massive influx of biological data offers up the possibility of better
predictions and models that demonstrate improved fidelity to wet-lab 
experiments.
It is through the development of algorithms that leverage the
structure of the data that we aim to cope with this increased throughput in computational 
biology and realize that goal.

\section{Acknowledgements}
This work is supported by the National Institutes of Health, under
grant GM108348.
Y.W.Y. is also supported by a Hertz Fellowship.
